PK object batch mode trial

### 2023-07-13 data-raw/batchMode_trial_gpm.Rmd
Updated get_winning_model and added files of TKstats, non-compartmental analysis for Pooled and Joint analyses for full `cvt` data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)

library(tidyverse, quietly = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
tidyverse_conflicts()
```

@@

```{r single_fit}
my_pk <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

@@

@@

# after fitting pk object for all cvt objects
# saveRDS(my_pk, file = "data-raw/all_cvt_pk.rds")
my_pk <- readRDS("data-raw/all_cvt_pk.rds")

my_tkstats <- get_tkstats(my_pk)
my_IC <- left_join(AIC(my_pk), BIC(my_pk))

@@

my_IC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "L-BFGS-B") %>%
  ungroup() %>%
  count(model)
# model_1comp 56
# model_2comp 50
# model_flat   5

@@

my_preds <- predict(my_pk)

@@

my_preds <- inner_join(winmodels, my_preds)

my_preds %>%
  rowwise() %>%
  mutate(Pred_Obs = Conc_trans/Conc_est) %>%
  filter(is.finite(Pred_Obs)) %>%
  ggplot(aes(x = Pred_Obs)) +
  geom_histogram(
                 fill = "grey5") +
  coord_cartesian(xlim =  c(0.001, 1000),
                  ylim = c(0, 2000)) +
  scale_y_continuous() +
  scale_x_log10()
  expand_limits(y = 0) +
  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
  annotate(geom = "text",
           x = 1.25, y = 1800,
           label = "88.4% of Observations\n within a factor of 2") +
  theme_classic() +
  labs(x = "Concentration Normalized to Average",
                y = "Number of Observations") +
  theme(panel.border = element_rect(color = "black", fill = NA),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.4))

# 89.9% of Pred_Obs are finite
# 64.5% Are below two-fold
# 26.3%  Are above two-fold
# 9.3% Are within twofold

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
set.seed(2023)
library(tidyverse, quietly = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
tidyverse_conflicts()
```

@@

```{r single_fit}
my_pk <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) # Add Reference for Joint Analysis

@@

get_winning_model(my_pk)

@@

# after fitting pk object for all cvt objects
# saveRDS(my_pk, file = "data-raw/all_cvt_pk.rds")
# saveRDS(my_pk, file = "data-raw/all_cvt_pk_JOINT.rds")
my_pk <- readRDS("data-raw/all_cvt_pk.rds")
my_AIC <- AIC(my_pk)
my_tkstats <- get_tkstats(my_pk)
my_IC <- left_join(AIC(my_pk), BIC(my_pk))

@@

my_IC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "L-BFGS-B") %>%
  ungroup() %>%
  filter(model == "model_flat") %>% pull(Chemical) %>% unique()
  count(model)
# model_1comp 56
# model_2comp 50
# model_flat   5

@@

my_preds <- predict(my_pk,
                    use_scale_conc = TRUE)

@@

my_preds <- inner_join(winmodels, my_preds)
my_tkstats <- inner_join(winmodels, my_tkstats)
my_nca <- get_nca(my_pk,
                  nca_group = vars(Chemical, Species,))
my_nca <- my_nca %>% dplyr::select(-param_sd_z, -param_units) %>%
  pivot_wider(names_from = param_name,
              values_from = param_value)

# Saving some CSVs
# my_tkstats %>% write_csv(file = "data-raw/Pooled_TKstats.csv")
# my_nca %>% write_csv(file = "data-raw/NonCompartmentalAnalysis.csv")

my_preds %>%
  rowwise() %>%
  mutate(Pred_Obs = Conc_trans/Conc_est) %>%
  filter(is.finite(Pred_Obs),
         model %in% c("model_1comp", "model_2comp")) %>%
  # mutate(pass = ifelse(Pred_Obs <= 2 & Pred_Obs >= 0.5, TRUE, FALSE)) %>%
  # pull(pass) %>% table()
  ggplot(aes(x = Pred_Obs)) +
  geom_histogram(binwidth = 0.4,
                 fill = "grey5") +
  scale_x_log10(limits = c(NA, 1E6)) +
  expand_limits(y = 0) +
  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
  facet_grid(cols = vars(model),
             rows = vars(Route)) +
  labs(x = "Predicted/Observed",
       y = "Number of Observations") +
  theme_classic() +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.4))

# 89.9% of Pred_Obs are finite
# 19.3% Are below two-fold
# 34.8%  Are above two-fold
# 45.9% Are within twofold

ggsave(paste0("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/",
              "PredictedObserved_compartmentModels_2023-07-11.png"),
       height = 4, width = 9)

# Pooled analysis
all_my_data %>% group_by(Chemical, Species, Reference, Media, Route) %>%
  filter(is.finite(Conc)) %>%
  summarise(OOM = log10(max(Conc) / min(Conc))) %>% 
  ggplot(aes(x = OOM)) +
  geom_histogram(bins = 15,
                 color = NA,
                 fill = "grey5") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5)) +
  labs(x = "Orders of Magnitude per Series\n log10(max/min)",
       y = "Count") +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        axis.ticks = element_blank(),
        axis.line = element_blank())

ggsave(paste0("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/",
              "OrdersOfMagnitude_2023-07-12.png"),
       height = 4, width = 4)

my_pk$prefit$fit_check %>% filter(fit_decision == "abort") %>%
  dplyr::select(model, Chemical) %>% distinct()

all_my_data %>%
  filter(Chemical == "DTXSID2021781")

my_AIC %>% group_by(Chemical, Species, method) %>%
  filter(if_any(contains("AIC"), ~ . == min(.)))
